14th International Satisfiability Modulo Theories Competition (SMT-COMP 2019): Rules and Procedures

### 2019-04-19 rules/rules19.tex
Removed track specific time limits.

\header{Time and memory limits.} \todo{Aina: Move all time and memory limits to the individual sections and forward reference from here}
%
Each SMT-COMP solver will be executed on a dedicated processor of a
competition machine, for each given benchmark, up to a fixed
wall-clock time limit~$T$.  Each processor has 4 cores.  Detailed
machine specifications are available on the competition web site.

The time limit~$T$ will be 40~minutes of wall-clock time per solver/benchmark
pair in the \maintrack, \inctrack and \ucoretrack, \todo{12 hours} in the
\challtrack, and \todo{40 + 5 as in Unsat core}~minutes in the \mvaltrack \footnote{The time limit may be
adjusted once we know the number of competition entrants and eligible
benchmarks.}  Solvers that take more than this time limit will be killed.
Solvers are allowed to spawn other processes; these will be killed at
approximately the same time as the first started process.

@@

>>>>

\header{Time and memory limits.}
%
Each SMT-COMP solver will be executed on a dedicated processor of a
competition machine, for each given benchmark, up to a fixed
wall-clock time limit~$T$. The individual track description specifies
the time limit for each track. Each processor has 4 cores.  Detailed
machine specifications are available on the competition web site.

@@

% The time limit~$T$ will be 40~minutes of wall-clock time per solver/benchmark
% pair in the \maintrack, \inctrack and \ucoretrack, \todo{12 hours} in the
% \challtrack, and \todo{40 + 5 as in Unsat core}~minutes in the \mvaltrack \footnote{The time limit may be
% adjusted once we know the number of competition entrants and eligible
% benchmarks.}  Solvers that take more than this time limit will be killed.
% Solvers are allowed to spawn other processes; these will be killed at
% approximately the same time as the first started process.
